### 2023-11-21 texts/paper_closing.tex
update t_coxzph in tex

% Created 2023-11-19 zo 22:29
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}

@@

% latex table generated in R 4.3.2 by xtable 1.8-4 package
% Sun Nov 19 21:58:11 2023
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_more}\\ 
 \hline
  \multicolumn{3}{l}{\textbf{Founder}} \\ 
 & Gender - Female & .31 \; (0.36) \\ 
   & Gender - Couple & -.07 \; (0.36) \\ 
   & Founder died & .11 \; (0.51) \\ 
   \multicolumn{3}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .76 \; (0.46) \\ 
   & Self-Identification - Collection & .52 \; (0.54) \\ 
   & Self-Identification - Other & 1.12 \; (0.36)^{**} \\ 
   & Founder name in Museum name & -.27 \; (0.31) \\ 
   & MOW inclusion & -.97 \; (0.40)^{*} \\ 
   \multicolumn{3}{l}{\textbf{Environment}} \\ 
 & PM density & -.03 \; (0.03) \\ 
   & PM density$^{2}$ & .00 \; (0.00) \\ 
   \hline
 & Museum-years & 7282 \\ 
   & Closures & 53 \\ 
   & log. Likelihood & -271.10 \\ 
   & AIC & 562.20 \\ 
   & BIC & 581.91 \\ 
   \hline 
 \multicolumn{3}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Cox Proportional Hazards Regression Results} 
\label{tbl:t_reg_coxph}
\end{table}

@@

% latex table generated in R 4.3.2 by xtable 1.8-4 package
% Sun Nov 19 21:58:05 2023
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{.}{.}{5}D{.}{.}{5}D{.}{.}{5}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Kaplan-Meier} & \multicolumn{1}{l}{Identity} & \multicolumn{1}{l}{Rank}\\ 
 \hline
  \multicolumn{2}{l}{\textbf{Founder}} \\ 
 & Founder Gender & .63 & .53 & .62 \\ 
   & Founder died & .68 & .64 & .87 \\ 
   \multicolumn{2}{l}{\textbf{Museum}} \\ 
 & Founder name in Museum name & .06 & .05 & .05^{*} \\ 
   & MOW inclusion & .39 & .43 & .59 \\ 
   & Self- Identification & .96 & .94 & .74 \\ 
   \multicolumn{2}{l}{\textbf{Environment}} \\ 
 & PM density & .78 & .80 & .81 \\ 
   & PM density$^{2}$ & .93 & .89 & .87 \\ 
   \multicolumn{2}{l}{\textbf{Miscellaneous}} \\ 
 & Global & .41 & .32 & .41 \\ 
   \hline 
 \multicolumn{3}{l}{\footnotesize{\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Z-test of proportional hazards} 
\label{tbl:t_coxzph}
\end{table}

>>>>

% Created 2023-11-21 di 10:37
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{article}

@@

% latex table generated in R 4.3.2 by xtable 1.8-4 package
% Tue Nov 21 10:36:10 2023
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_more}\\ 
 \hline
  \multicolumn{3}{l}{\textbf{Founder}} \\ 
 & Gender - Female & .31 \; (0.36) \\ 
   & Gender - Couple & -.07 \; (0.36) \\ 
   & Founder died & .11 \; (0.51) \\ 
   \multicolumn{3}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .76 \; (0.46) \\ 
   & Self-Identification - Collection & .52 \; (0.54) \\ 
   & Self-Identification - Other & 1.12 \; (0.36)^{**} \\ 
   & Founder name in Museum name & -.27 \; (0.31) \\ 
   & MOW inclusion & -.97 \; (0.40)^{*} \\ 
   \multicolumn{3}{l}{\textbf{Environment}} \\ 
 & PM density & -.03 \; (0.03) \\ 
   & PM density$^{2}$ & .00 \; (0.00) \\ 
   \hline
 & Museum-years & 7282 \\ 
   & Closures & 53 \\ 
   & log. Likelihood & -271.10 \\ 
   & AIC & 562.20 \\ 
   & BIC & 581.91 \\ 
   \hline 
 \multicolumn{3}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Cox Proportional Hazards Regression Results} 
\label{tbl:t_reg_coxph}
\end{table}

@@

% latex table generated in R 4.3.2 by xtable 1.8-4 package
% Tue Nov 21 10:36:04 2023
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{.}{.}{5}D{.}{.}{5}D{.}{.}{5}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Kaplan-Meier} & \multicolumn{1}{l}{Identity} & \multicolumn{1}{l}{Rank}\\ 
 \hline
  \multicolumn{2}{l}{\textbf{Founder}} \\ 
 & Founder died & .68 & .64 & .87 \\ 
   & Gender - Couple & .35 & .26 & .35 \\ 
   & Gender - Female & .67 & .73 & .60 \\ 
   \multicolumn{2}{l}{\textbf{Museum}} \\ 
 & Founder name in Museum name & .06 & .05 & .05^{*} \\ 
   & MOW inclusion & .39 & .43 & .59 \\ 
   & Self-Identification - Collection & .72 & .64 & .44 \\ 
   & Self-Identification - Foundation & .78 & .90 & .73 \\ 
   & Self-Identification - Other & .76 & .79 & .63 \\ 
   \multicolumn{2}{l}{\textbf{Environment}} \\ 
 & PM density & .78 & .80 & .81 \\ 
   & PM density$^{2}$ & .93 & .89 & .87 \\ 
   \multicolumn{2}{l}{\textbf{Miscellaneous}} \\ 
 & Global & .41 & .32 & .41 \\ 
   \hline 
 \multicolumn{3}{l}{\footnotesize{\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Z-test of proportional hazards} 
\label{tbl:t_coxzph}
\end{table}
